Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-01-02 p2/p2.Rmd
.

---
title: "Adaption of the Chumbley Score to matching of bullet striation marks"
authors:
- affiliation: Department of Statistics, Iowa State University 
  name: Ganesh Krishnan
  thanks: The authors gratefully acknowledge ...
- affiliation: Department of Statistics and csafe, Iowa State University 
  name: Heike Hofmann
biblio-style: apsr
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    keep_tex: yes
    latex_engine: pdflatex
    template: template.tex
  html_document: default
blinded: 0
keywords:
- 3 to 6 keywords
- that do not appear in the title
bibliography: bibliography
abstract: null
---

@@

```{r, fig.cap="Type II errors for different levels of coarseness. XXX We need more values around .25"}
errors2 %>% filter(wv==30)%>% ggplot(aes(x = coarse, y=beta, colour=factor(alpha))) +
  geom_point() + geom_line() +
  theme_bw() +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha), palette="Set2")
```

>>>>

---
title: "Adaption of the Chumbley Score to matching of bullet striation marks"
authors:
- affiliation: Department of Statistics, Iowa State University 
  name: Ganesh Krishnan
  thanks: The authors gratefully acknowledge ...
- affiliation: Department of Statistics and CSAFE, Iowa State University 
  name: Heike Hofmann
biblio-style: apsr
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    keep_tex: yes
    latex_engine: pdflatex
    template: template.tex
  html_document: default
blinded: 0
keywords:
- 3 to 6 keywords
- that do not appear in the title
bibliography: bibliography
abstract: null
---

@@

```{r, fig.cap="Type II errors for different levels of coarseness."}
errors2 %>% filter(wv==30)%>% ggplot(aes(x = coarse, y=beta, colour=factor(alpha))) +
  geom_point() + geom_line() +
  theme_bw() +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha), palette="Set2")
```
